### 2008-09-10 developments/PIC16C432/PDB/PIC.tex

\bf MACHINE

@@

\hspace*{0.20in}\it TYPES\rm ,

\hspace*{0.20in}\it BIT\_VECTOR\_DEFINITION\rm ,

\hspace*{0.20in}\it BIT\_VECTOR\_ARITHMETICS\rm ,

\hspace*{0.20in}\it BYTE\_DEFINITION

@@

\hspace*{0.20in}\it add\rm , \it substract\rm ,

\hspace*{0.20in}\it and\rm , \it ior\rm , \it xor\rm ,

\hspace*{0.20in}\it bitclear\rm , \it bitset\rm , \it bitget\rm ,

\hspace*{0.20in}\it complement\rm , \it swap\rm , \it rotateleft\rm , \it rotateright

@@

\hspace*{0.20in}\it add \rm : \rm (\it UCHAR  $\times$  \it UCHAR\rm )  $\fun$  \rm (\it UCHAR  $\times$  \bf BOOL  $\times$  \bf BOOL  $\times$  \bf BOOL\rm )  $\land$

\vspace*{4mm}
\hspace*{0.20in}\it substract \rm : \rm (\it UCHAR  $\times$  \it UCHAR\rm )  $\fun$  \rm (\it UCHAR  $\times$  \bf BOOL  $\times$  \bf BOOL\rm )  $\land$

\hspace*{0.20in} $\forall$  \rm (\it w1\rm , \it w2\rm , \it diff\rm )\rm .

\hspace*{0.30in}\rm (\it w1  $\in$  \it UCHAR  $\land$  \it w2  $\in$  \it UCHAR  $\land$  \it diff  $\in$   $\int$   $\land$  \it diff \rm = \it w1\rm -\it w2  $\implies$

\hspace*{0.40in}\rm (\rm (\it diff $<$ \rm 0  $\implies$  \it substract\rm (\it w1\rm , \it w2\rm ) \rm = \rm (\it diff\rm +\rm 2\rm 5\rm 6\rm , \bf FALSE\rm , \bf TRUE\rm )\rm )  $\land$

\hspace*{0.45in}\rm (\it diff  $\geq$  \rm 0  $\implies$  \it substract\rm (\it w1\rm , \it w2\rm ) \rm = \rm (\it diff\rm , \bf bool\rm (\it diff\rm =\rm 0\rm )\rm , \bf FALSE\rm )\rm )\rm )\rm )  $\land$

\hspace*{0.20in}\it and \rm : \rm (\it BYTE  $\times$  \it BYTE\rm )  $\fun$  \rm (\it BYTE  $\times$  \bf BOOL\rm )  $\land$

\hspace*{0.20in} $\forall$  \rm (\it w1\rm , \it w2\rm , \it ww\rm )\rm .

\hspace*{0.30in}\rm (\it w1  $\in$  \it BYTE  $\land$  \it w2  $\in$  \it BYTE  $\land$  \it ww  $\in$  \it BYTE  $\land$  \it ww \rm = \it bv\_and\rm (\it w1\rm , \it w2\rm )  $\implies$

\hspace*{0.60in}\it and\rm (\it w1\rm , \it w2\rm ) \rm = \rm (\it ww\rm , \bf bool\rm (\it bv\_to\_nat\rm (\it ww\rm ) \rm = \rm 0\rm )\rm )\rm )  $\land$

\hspace*{0.20in}\it ior \rm : \rm (\it BYTE  $\times$  \it BYTE\rm )  $\fun$  \rm (\it BYTE  $\times$  \bf BOOL\rm )  $\land$

\hspace*{0.20in} $\forall$  \rm (\it w1\rm , \it w2\rm , \it ww\rm )\rm .

\hspace*{0.30in}\rm (\it w1  $\in$  \it BYTE  $\land$  \it w2  $\in$  \it BYTE  $\land$  \it ww  $\in$  \it BYTE  $\land$  \it ww \rm = \it bv\_or\rm (\it w1\rm , \it w2\rm )  $\implies$

\hspace*{0.60in}\it ior\rm (\it w1\rm , \it w2\rm ) \rm = \rm (\it ww\rm , \bf bool\rm (\it bv\_to\_nat\rm (\it ww\rm ) \rm = \rm 0\rm )\rm )\rm )  $\land$

\hspace*{0.20in}\it xor \rm : \rm (\it BYTE  $\times$  \it BYTE\rm )  $\fun$  \rm (\it BYTE  $\times$  \bf BOOL\rm )  $\land$

\hspace*{0.20in} $\forall$  \rm (\it w1\rm , \it w2\rm , \it ww\rm )\rm .

\hspace*{0.30in}\rm (\it w1  $\in$  \it BYTE  $\land$  \it w2  $\in$  \it BYTE  $\land$  \it ww  $\in$  \it BYTE  $\implies$

\hspace*{0.40in}\rm (\it ww \rm = \it bv\_xor\rm (\it w1\rm , \it w2\rm )  $\implies$

\hspace*{0.60in}\it xor\rm (\it w1\rm , \it w2\rm ) \rm = \rm (\it ww\rm , \bf bool\rm (\it bv\_to\_nat\rm (\it ww\rm ) \rm = \rm 0\rm )\rm )\rm )\rm )  $\land$

\hspace*{0.20in}\it bitget \rm : \rm (\it BYTE  $\times$  \it BYTE\_INDEX\rm )  $\fun$  \it BIT  $\land$

\hspace*{0.20in} $\forall$  \rm (\it ww\rm , \it ii\rm )\rm .\rm (\it ww  $\in$  \it BYTE  $\land$  \it ii  $\in$  \it BYTE\_INDEX  $\implies$  \it bitget\rm (\it ww\rm ,\it ii\rm ) \rm = \it ww\rm (\it ii\rm )\rm )  $\land$

\hspace*{0.20in}\it bitset \rm : \rm (\it BYTE  $\times$  \it BYTE\_INDEX\rm )  $\fun$  \it BYTE  $\land$

\hspace*{0.20in} $\forall$  \rm (\it ww\rm , \it ii\rm )\rm .\rm (\it ww  $\in$  \it BYTE  $\land$  \it ii  $\in$  \it BYTE\_INDEX  $\implies$  \it bitset\rm (\it ww\rm ,\it ii\rm ) \rm = \it bv\_set\rm (\it ww\rm , \it ii\rm )\rm )  $\land$

\hspace*{0.20in}\it bitclear \rm : \rm (\it BYTE  $\times$  \it BYTE\_INDEX\rm )  $\fun$  \it BYTE  $\land$

\hspace*{0.20in} $\forall$  \rm (\it ww\rm , \it ii\rm , \it bb\rm )\rm .\rm (\it ww  $\in$  \it BYTE  $\land$  \it ii  $\in$  \it BYTE\_INDEX  $\land$  \it bb  $\in$  \it BIT  $\implies$  \it bitclear\rm (\it ww\rm ,\it ii\rm ) \rm = \it bv\_clear\rm (\it ww\rm , \it ii\rm )\rm )  $\land$

\hspace*{0.20in}\it complement  $\in$  \it BYTE  $\fun$  \it BYTE  $\land$

\hspace*{0.20in} $\forall$  \rm (\it ww\rm )\rm .\rm (\it ww  $\in$  \it BYTE  $\implies$  \it complement\rm (\it ww\rm ) \rm = \it bv\_not\rm (\it ww\rm )\rm )  $\land$

\hspace*{0.20in}\it swap  $\in$  \it BYTE  $\fun$  \it BYTE  $\land$

\hspace*{0.20in} $\forall$  \rm (\it ww\rm )\rm .\rm (\it ww  $\in$  \it BYTE  $\implies$

\hspace*{0.30in}\rm (\it swap\rm (\it ww\rm ) \rm = \rm \{\rm 0 $\mapsto$ \it ww\rm (\rm 4\rm )\rm , \rm 1 $\mapsto$ \it ww\rm (\rm 5\rm )\rm , \rm 2 $\mapsto$ \it ww\rm (\rm 6\rm )\rm , \rm 3 $\mapsto$ \it ww\rm (\rm 7\rm )\rm , \rm 4 $\mapsto$ \it ww\rm (\rm 0\rm )\rm , \rm 5 $\mapsto$ \it ww\rm (\rm 1\rm )\rm , \rm 6 $\mapsto$ \it ww\rm (\rm 2\rm )\rm , \rm 7 $\mapsto$ \it ww\rm (\rm 3\rm )\rm \}\rm )\rm )  $\land$

\hspace*{0.20in}\it rotateleft  $\in$  \it BYTE  $\fun$  \it BYTE  $\times$  \bf BOOL  $\land$

\hspace*{0.20in} $\forall$  \rm (\it ww\rm )\rm .\rm (\it ww  $\in$  \it BYTE  $\implies$

\hspace*{0.30in}\rm (\it rotateleft\rm (\it ww\rm ) \rm = \rm (\rm \{\rm 0 $\mapsto$ \it ww\rm (\rm 7\rm )\rm , \rm 1 $\mapsto$ \it ww\rm (\rm 0\rm )\rm , \rm 2 $\mapsto$ \it ww\rm (\rm 1\rm )\rm , \rm 3 $\mapsto$ \it ww\rm (\rm 2\rm )\rm , \rm 4 $\mapsto$ \it ww\rm (\rm 3\rm )\rm , \rm 5 $\mapsto$ \it ww\rm (\rm 4\rm )\rm , \rm 6 $\mapsto$ \it ww\rm (\rm 5\rm )\rm , \rm 7 $\mapsto$ \it ww\rm (\rm 6\rm )\rm \}\rm ,

\hspace*{0.80in}\bf bool\rm (\it ww\rm (\rm 7\rm )\rm =\rm 1\rm )\rm )\rm )\rm )  $\land$

\hspace*{0.20in}\it rotateright  $\in$  \it BYTE  $\fun$  \it BYTE  $\times$  \bf BOOL\hspace*{0.10in} $\land$

\hspace*{0.20in} $\forall$  \rm (\it ww\rm )\rm .\rm (\it ww  $\in$  \it BYTE\hspace*{0.10in} $\implies$

\hspace*{0.30in}\rm (\it rotateright\rm (\it ww\rm ) \rm = \rm (\rm \{\rm 0 $\mapsto$ \it ww\rm (\rm 1\rm )\rm , \rm 1 $\mapsto$ \it ww\rm (\rm 2\rm )\rm , \rm 2 $\mapsto$ \it ww\rm (\rm 3\rm )\rm , \rm 3 $\mapsto$ \it ww\rm (\rm 4\rm )\rm , \rm 4 $\mapsto$ \it ww\rm (\rm 5\rm )\rm , \rm 5 $\mapsto$ \it ww\rm (\rm 6\rm )\rm , \rm 6 $\mapsto$ \it ww\rm (\rm 7\rm )\rm , \rm 7 $\mapsto$ \it ww\rm (\rm 0\rm )\rm \}\rm ,

\hspace*{0.80in}\bf bool\rm (\it ww\rm (\rm 0\rm )\rm =\rm 1\rm )\rm )\rm )\rm )

\vspace*{4mm}
\bf ASSERTIONS

\hspace*{0.20in}\bf dom\rm (\it add\rm ) \rm = \it UCHAR  $\times$  \it UCHAR\rm ;

\hspace*{0.20in}\bf ran\rm (\it add\rm )  $\subseteq$  \it UCHAR  $\times$  \bf BOOL  $\times$  \bf BOOL  $\times$  \bf BOOL\rm ;

\hspace*{0.20in}\bf dom\rm (\it substract\rm ) \rm = \it UCHAR  $\times$  \it UCHAR\rm ;

\hspace*{0.20in}\bf ran\rm (\it substract\rm )  $\subseteq$  \it UCHAR  $\times$  \bf BOOL  $\times$  \bf BOOL\rm ;

\hspace*{0.20in}\bf dom\rm (\it and\rm ) \rm = \it BYTE  $\times$  \it BYTE\rm ;

\hspace*{0.20in}\bf ran\rm (\it and\rm )  $\subseteq$  \it BYTE  $\times$  \bf BOOL\rm ;

\hspace*{0.20in}\bf dom\rm (\it ior\rm ) \rm = \it BYTE  $\times$  \it BYTE\rm ;

\hspace*{0.20in}\bf ran\rm (\it ior\rm )  $\subseteq$  \it BYTE  $\times$  \bf BOOL\rm ;

\hspace*{0.20in}\bf dom\rm (\it xor\rm ) \rm = \it BYTE  $\times$  \it BYTE\rm ;

\hspace*{0.20in}\bf ran\rm (\it xor\rm )  $\subseteq$  \it BYTE  $\times$  \bf BOOL\rm ;

\hspace*{0.20in}\bf dom\rm (\it bitclear\rm ) \rm = \it BYTE  $\times$  \it BYTE\_INDEX\rm ;

\hspace*{0.20in}\bf ran\rm (\it bitclear\rm )  $\subseteq$  \it BYTE\rm ;

\hspace*{0.20in}\bf dom\rm (\it bitset\rm ) \rm = \it BYTE  $\times$  \it BYTE\_INDEX\rm ;

\hspace*{0.20in}\bf ran\rm (\it bitset\rm )  $\subseteq$  \it BYTE\rm ;

\hspace*{0.20in}\bf dom\rm (\it bitget\rm ) \rm = \it BYTE  $\times$  \it BYTE\_INDEX\rm ;

\hspace*{0.20in}\bf ran\rm (\it bitget\rm )  $\subseteq$  \it BIT\rm ;

\hspace*{0.20in}\bf dom\rm (\it complement\rm ) \rm = \it BYTE\rm ;

\hspace*{0.20in}\bf ran\rm (\it complement\rm )  $\subseteq$  \it BYTE\rm ;

\hspace*{0.20in}\bf dom\rm (\it swap\rm ) \rm = \it BYTE\rm ;

\hspace*{0.20in}\bf ran\rm (\it swap\rm )  $\subseteq$  \it BYTE\rm ;

\hspace*{0.20in}\bf ran\rm (\it rotateleft\rm )  $\subseteq$  \it BYTE  $\times$  \bf BOOL\rm ;

\hspace*{0.20in}\bf dom\rm (\it rotateleft\rm ) \rm = \it BYTE\rm ;

\hspace*{0.20in}\bf dom\rm (\it rotateright\rm ) \rm = \it BYTE\rm ;

\hspace*{0.20in}\bf ran\rm (\it rotateright\rm )  $\subseteq$  \it BYTE  $\times$  \bf BOOL\rm ;

@@

\hspace*{0.20in}\it add\rm (\rm 0\rm ,\rm 0\rm ) \rm = \rm (\rm 0\rm , \bf TRUE\rm , \bf FALSE\rm , \bf FALSE\rm )\rm ;

\hspace*{0.20in}\it add\rm (\rm 2\rm 5\rm 5\rm ,\rm 1\rm ) \rm = \rm (\rm 0\rm , \bf TRUE\rm , \bf FALSE\rm , \bf TRUE\rm )

>>>>

\vspace*{4mm}
\bf MACHINE

\hspace*{0.20in}\it PIC

\hspace*{0.20in}\it BYTE\_DEFINITION\rm ,

\hspace*{0.20in}\it TYPES

\vspace*{4mm}
\bf USES

@@

\vspace*{4mm}
\bf INCLUDES

\hspace*{0.20in}\it DATA\_MEMORY

\vspace*{4mm}
\bf VARIABLES

\hspace*{0.20in}\it W\_REGISTER\rm ,

\hspace*{0.20in}\it pc\rm ,

\hspace*{0.20in}\it stack\rm ,

\hspace*{0.20in}\it sp

\vspace*{4mm}
\bf INVARIANT

\hspace*{0.20in}\it W\_REGISTER  $\in$  \it BYTE  $\land$

\hspace*{0.20in}\it pc  $\in$  \it INSTRUCTION  $\land$

\hspace*{0.20in}\it sp  $\in$   $\nat$   $\land$

\hspace*{0.20in}\it stack  $\in$   $\nat$   $\pfun$  \it INSTRUCTION  $\land$

\hspace*{0.20in}\bf dom\rm (\it stack\rm ) \rm = \rm 0 $\upto$ \rm (\it sp\rm -\rm 1\rm )

@@

\hspace*{0.20in}

\hspace*{0.20in}\it TO\_POS\rm , \it PD\_POS\rm ,

\hspace*{0.20in}\it ZERO\_POS\rm , \it DCARRY\_POS\rm , \it CARRY\_POS\rm ,

\hspace*{0.20in}\it get\_address\rm ,

\hspace*{0.20in}\it get\_offset

@@

@@

\hspace*{0.20in}\it TO\_POS  $\in$  \it BYTE\_INDEX  $\land$ \hspace*{0.20in}\it TO\_POS \rm = \rm 4  $\land$

\hspace*{0.20in}\it PD\_POS  $\in$  \it BYTE\_INDEX  $\land$ \hspace*{0.20in}\it PD\_POS \rm = \rm 3  $\land$

\hspace*{0.20in}\it ZERO\_POS  $\in$  \it BYTE\_INDEX  $\land$ \hspace*{0.20in}\it ZERO\_POS \rm = \rm 2  $\land$

\hspace*{0.20in}\it DCARRY\_POS  $\in$  \it BYTE\_INDEX  $\land$ \hspace*{0.20in}\it DCARRY\_POS \rm = \rm 1  $\land$

\hspace*{0.20in}\it CARRY\_POS  $\in$  \it BYTE\_INDEX  $\land$ \hspace*{0.20in}\it CARRY\_POS \rm = \rm 0

\vspace*{4mm}
\bf INITIALISATION

\hspace*{0.20in}\it W\_REGISTER  $:\in$  \it BYTE  $\para$

\hspace*{0.20in}\it pc  $:\in$  \it INSTRUCTION  $\para$

\hspace*{0.20in}\it stack \rm :=  $\ensembleVide$   $\para$

\hspace*{0.20in}\it sp \rm := \rm 0

\vspace*{4mm}
\bf OPERATIONS

\hspace*{0.20in}\bf CALL \rm (\it kk\rm ) \rm =

\hspace*{0.40in}\bf PRE \it kk  $\in$  \it INSTRUCTION \bf THEN

\hspace*{0.60in}\bf stack\rm (\it sp\rm ) \rm := \it instruction\_next\rm (\it pc\rm )  $\para$

\hspace*{0.60in}\it sp \rm := \it sp \rm + \rm 1  $\para$

\hspace*{0.60in}\it pc \rm := \it kk

\hspace*{0.40in}\bf END

\hspace*{0.20in}\rm ;

\hspace*{0.20in}\bf RETURN \rm =

\hspace*{0.40in}\bf PRE \it sp $>$ \rm 0 \bf THEN

\hspace*{0.60in}\it stack \rm := \rm \{\it sp \rm - \rm 1\rm \}  $\ndres$  \it stack  $\para$

\hspace*{0.60in}\it pc \rm := \it stack\rm (\it sp \rm - \rm 1\rm )  $\para$

\hspace*{0.60in}\it sp \rm := \it sp \rm - \rm 1

\hspace*{0.40in}\bf END

\hspace*{0.20in}\rm ;

\hspace*{0.20in}\bf RETLW \rm (\it kk\rm ) \rm =

\hspace*{0.40in}\bf PRE \it kk  $\in$  \it UCHAR  $\land$  \it sp $>$ \rm 0 \bf THEN

\hspace*{0.60in}\it pc \rm := \it stack\rm (\it sp \rm - \rm 1\rm )  $\para$

\hspace*{0.60in}\it W\_REGISTER \rm := \it uchar\_to\_byte\rm (\it kk\rm )

\hspace*{0.40in}\bf END

\hspace*{0.20in}\rm ;

\hspace*{0.20in}\bf ADDLW \rm (\it kk\rm ) \rm =

\hspace*{0.40in}\bf PRE \it kk  $\in$  \it UCHAR \bf THEN

\hspace*{0.60in}\bf ANY \it result\rm , \it carry\rm , \it digit\_carry\rm , \it zero \bf WHERE

\hspace*{0.80in}\it result  $\in$  \it UCHAR  $\land$  \it digit\_carry  $\in$  \bf BOOL  $\land$  \it carry  $\in$  \bf BOOL  $\land$  \it zero  $\in$  \bf BOOL  $\land$

\hspace*{0.80in}\it result\rm , \it digit\_carry\rm , \it carry\rm , \it zero \rm = \it add\rm (\it kk\rm , \it byte\_to\_uchar\rm (\it W\_REGISTER\rm )\rm )

\hspace*{0.60in}\bf THEN

\hspace*{0.80in}\it W\_REGISTER \rm := \it uchar\_to\_byte\rm (\it result\rm )  $\para$

\hspace*{0.80in}\it mem \rm := \it update\_status\rm (\it zero\rm , \it digit\_carry\rm , \it carry\rm )

\hspace*{0.60in}\bf END  $\para$

\hspace*{0.60in}\it pc \rm := \it instruction\_next\rm (\it pc\rm )

\hspace*{0.40in}\bf END

\hspace*{0.20in}\rm ;

\hspace*{0.20in}\bf ADDWF \rm (\it ff\rm , \it dd\rm ) \rm =

\hspace*{0.40in}\bf PRE \it ff  $\in$  \it REGISTER0  $\land$  \it dd  $\in$  \it BIT \bf THEN

\hspace*{0.60in}\bf ANY \it dest\rm , \it result\rm , \it carry\rm , \it digit\_carry\rm , \it zero \bf WHERE

\hspace*{0.80in}\it dest  $\in$  \it REGISTER  $\land$

\hspace*{0.80in}\it result  $\in$  \it UCHAR  $\land$  \it digit\_carry  $\in$  \bf BOOL  $\land$  \it carry  $\in$  \bf BOOL  $\land$  \it zero  $\in$  \bf BOOL  $\land$

\hspace*{0.80in}\it dest \rm = \it get\_address\rm (\it ff\rm , \it RP0\_VAL\rm , \it byte\_to\_uchar\rm (\it FSR\_VAL\rm )\rm )  $\land$

\hspace*{0.80in}\it result\rm , \it digit\_carry\rm , \it carry\rm , \it zero \rm = \it add\rm (\it byte\_to\_uchar\rm (\it mem\rm (\it dest\rm )\rm )\rm , \it byte\_to\_uchar\rm (\it W\_REGISTER\rm )\rm )

\hspace*{0.60in}\bf THEN

\hspace*{0.80in}\bf ANY \it mem2\rm , \it bv \bf WHERE

\hspace*{1.00in}\it bv  $\in$  \it BYTE  $\land$  \it bv \rm = \it uchar\_to\_byte\rm (\it result\rm )  $\land$

\hspace*{1.00in}\it mem2  $\in$  \it REGISTER  $\fun$  \it BYTE  $\land$

\hspace*{1.00in}\rm (\it dd  $\not =$  \rm 0  $\land$  \it dest  $\not\in$  \it UNIMPLEMENTED\_LOCATIONS  $\implies$  \it mem2 \rm = \it mem  $\lover$  \rm \{ \it dest  $\mapsto$  \it bv \rm \}\rm )  $\land$

\hspace*{1.00in}\rm (\it dd \rm = \rm 0  $\lor$  \it dest  $\in$  \it UNIMPLEMENTED\_LOCATIONS  $\implies$  \it mem2 \rm = \it mem\rm )

\hspace*{0.80in}\bf THEN

\hspace*{1.00in}\bf IF \it dd \rm = \rm 0 \bf THEN

\hspace*{1.20in}\it W\_REGISTER \rm := \it bv

\hspace*{1.00in}\bf END  $\para$

\hspace*{1.00in}\bf IF \it ff  $\not =$  \it STATUS\_ADDR0 \bf THEN

\hspace*{1.20in}\it mem \rm := \it update\_status\rm (\it zero\rm , \it digit\_carry\rm , \it carry\rm )

\hspace*{1.00in}\bf END

\hspace*{0.80in}\bf END

\hspace*{0.60in}\bf END  $\para$

\hspace*{0.60in}\it pc \rm := \it instruction\_next\rm (\it pc\rm )

\hspace*{0.40in}\bf END
